# Outline

::: {.larger2}

* Overview of package functionality

* Discussion for ggplot2-extenders 

:::

# Data

Examples use a labeled version of the `survival::colon` data set.

::: columns
::: {.column width="50%"}
```{r}
library(ggsurvfit)
library(gtsummary)
library(tidyverse)

df_colon <- df_colon |> select(time, status, surg)
df_colon
```
:::

::: {.column width="50%"}
```{r}
df_colon |> 
  tbl_summary()
```
:::
:::

# Basic Example

::: columns
::: {.column width="80%"}

```{r}
survfit2(Surv(time, status) ~ surg, data = df_colon) |> 
  ggsurvfit() +
  add_risktable()
```

:::
::: {.column width="20%"}
::: {.smaller}
::: {.incremental}

* The Good
  - Simple code and figure is nearly publishable
  - Risk table with both no. at risk and events easily added
  - x-axis label taken from the `time` column label
  - Can use **ggplot2** `+` notation

  
* The Could-Be-Better
  - Y-axis label is incorrect, and the range of axis is best 0-100%
  - Axis padding a bit more than I prefer for a Kaplan-Meier figure
  - X-axis typically has more tick marks for Kaplan-Meier figure

:::
:::
:::
:::

# Basic Example

```{r}
survfit2(Surv(time, status) ~ surg, data = df_colon) |> 
  ggsurvfit() +
  add_risktable() +
  scale_ggsurvfit() +
  labs(y = "Recurrence-free Probability")
```













