# Outline

::: {.larger2}

* **Overview of package functionality**

* Discussion for ggplot2-extenders 

:::

# Data

Examples use a labeled version of the `survival::colon` data set.

```{r}
#| echo: false
list(`as_gt-lst:addl_cmds` = list(tab_spanner = rlang::expr(gt::tab_options(table.font.size = 22)))) |> 
  gtsummary::set_gtsummary_theme()
```

::: columns
::: {.column width="50%"}
```{r}
library(ggsurvfit)
library(gtsummary)
library(tidyverse)

df_colon <- df_colon |> select(time, status, surg)
df_colon
```
:::

::: {.column width="50%"}
```{r}
#| freeze: false
df_colon |> 
  tbl_summary()
```
:::
:::

# Basic Example

::: columns
::: {.column width="80%"}

```{r}
survfit2(Surv(time, status) ~ surg, data = df_colon) |> 
  ggsurvfit() +
  add_risktable()
```

:::
::: {.column width="20%"}
::: {.smaller}
::: {.incremental}

* The Good
  - Simple code and figure is nearly publishable
  - Risk table with both no. at risk and events easily added
  - x-axis label taken from the `time` column label
  - Can use **ggplot2** `+` notation

  
* The Could-Be-Better
  - y-axis label is incorrect, and the range of axis is best at 0-100%
  - Axis padding a bit more than I prefer for a Kaplan-Meier figure
  - x-axis typically has more tick marks for Kaplan-Meier figure

:::
:::
:::
:::

# Basic Example

::: columns
::: {.column width="80%"}
```{r}
#| code-line-numbers: "4-5"
survfit2(Surv(time, status) ~ surg, data = df_colon) |> 
  ggsurvfit() +
  add_risktable() +
  scale_ggsurvfit() +
  labs(y = "Recurrence-free Progression")
```

:::
::: {.column width="20%"}
::: {.smaller}
::: {.incremental}

* Padding has been reduced and curves begin in the upper left corner of plot

* x-axis reports additional time points (and as a result, the risk table as well)

* We updated the y-axis label weaving standard **ggplot2** functions

:::
:::
:::
:::


# Basic Example

::: columns
::: {.column width="80%"}
```{r}
#| code-line-numbers: "6"
survfit2(Surv(time, status) ~ surg, data = df_colon) |> 
  ggsurvfit() +
  add_risktable() +
  scale_ggsurvfit() +
  labs(y = "Recurrence-free Progression") +
  ggeasy::easy_move_legend("top")
```

:::
::: {.column width="20%"}
::: {.smaller}

* Padding has been reduced and curves begin in the upper left corner of plot

* x-axis reports additional time points (and as a result, the risk table as well)

* We updated the y-axis label weaving standard **ggplot2** functions

* We can even use ggplot2-extender functions

:::
:::
:::


# Another Example

```{r}
#| output-location: slide
#| code-line-numbers: "|2|3|4-5|6|7|8|10-12"
survfit2(Surv(time, status) ~ surg, data = df_colon) |>
  ggsurvfit(type = "risk", linewidth = 1.2) +
  add_confidence_interval() +
  add_risktable(risktable_stats = "n.risk") +
  add_risktable_strata_symbol(symbol = "\U25CF", size = 17) +
  add_quantile(x_value = 5, linetype = "dotted", linewidth = 0.8) +
  add_censor_mark(size = 2, alpha = 0.2) +
  add_pvalue(caption = "Log-rank {p.value}") +
  scale_ggsurvfit() +
  scale_color_manual(values = c('#54738E', '#82AC7C')) +
  scale_fill_manual(values = c('#54738E', '#82AC7C')) +
  labs(y = "Risk of Recurrence")
```



