# Outline

::: {.larger2}

* Overview of package functionality

* **Discussion for ggplot2-extenders**

    - Side-by-side plots with {patchwork}

    - Structure of {ggsurvfit} functions
    
:::

# Side-by-Side

::: columns
::: {.column width="50%"}

```{r}
library(ggsurvfit)
library(patchwork)

p <-
  survfit2(Surv(time, status) ~ 1, df_colon) |> 
  ggsurvfit() +
  add_confidence_interval() +
  add_risktable() +
  scale_ggsurvfit()
```

:::
::: {.column width="50%"}

```{r}
# build plot (which constructs the risktable)
built_p <- ggsurvfit_build(p)

# wrap built plot to place side-by-side
p2 <- 
  wrap_elements(built_p) | 
  wrap_elements(built_p)
```

:::
:::

```{r}
#| echo: false
#| fig-height: 3
p2
```

::: {.notes}
The risk tables are not built until print or running `ggsurvfit_build()`

Then you have to wrap the 
:::

# Side-by-Side

How can we make this easier for **ggsurvfit** users?

- IDEA 1

  - In **patchwork**, the first line the arithmetic operator is a conditional to assess if the object needs processing

  - We could make this operation an exported generic function!
  
  - Issue submitted in Nov 2022, but no response yet. [https://github.com/thomasp85/patchwork/issues/310](https://github.com/thomasp85/patchwork/issues/310)

# Side-by-Side

::: columns
::: {.column width="20%"}

Current **patchwork**
<br><br><br>
<br><br><br>
Proposed **patchwork**

:::
::: {.column width="80%"}

```r
if (should_autowrap(e2)) e2 <- wrap_elements(full = e2) 

should_autowrap <- function(x) {
    is.grob(x) || inherits(x, 'formula') || is.raster(x) || inherits(x, 'nativeRaster')
  }
```

<br>

```r
#' @export
#' @rdname arithmetic_prep
arithmetic_prep <- function(x, ...) {
  UseMethod("arithmetic_prep")
}

#' @export
#' @rdname arithmetic_prep
arithmetic_prep.default <- function(x, ...) {
  # wrap input plot as needed
  if (is.grob(x) || inherits(x, 'formula') || is.raster(x) || inherits(x, 'nativeRaster')) {
    x <- wrap_elements(full = x)
  }
  x
}
```

:::
:::

::: {.notes}
Any tips on getting this through??
:::

# Side-by-Side

- IDEA 2: S4 😬😬😬   

  - I reached out on Stack Overflow, but couldn't get the S4 solution to work
  
  - Also, I don't know anything about S4 🤷
  
  - https://stackoverflow.com/questions/74072102
  
  
# Function Stucture

- The package's functions work! Nice!

- I think I may have implemented it in a strange way.

- Is there better way? 🤔🤔

# Function Stucture

```r
add_censor_mark <- function(...) {
  add_censor_mark_empty_list <- list()
  structure(add_censor_mark_empty_list,
            dots = utils::modifyList(x = list(na.rm = TRUE, size = 2, shape = 3),
                                     val = rlang::dots_list(...)),
            class = "add_censor_mark")
}

ggplot_add.add_censor_mark <- function (object, plot, object_name) {
  update_add_censor_mark(plot, object)
}

update_add_censor_mark <- function(p, add_censor_mark_empty_list) {
  # getting user-passed arguments
  dots <- attr(add_censor_mark_empty_list, "dots")

  # add censor marks with `geom_point()`
  p +
    rlang::inject(
      ggplot2::geom_point(
        data = ~ tidyr::uncount(.x, weights = .data$n.censor),
        ggplot2::aes(!!!.construct_censor_mark_aes(p)),
        !!!dots
      )
    )
}
```
